M.Sc. Proposal: \\ \bigskip Computational Electrokinetics

### 2012-02-01 notes/work/ch02.tex
Nondimensionalization.
Add numerical results.

The problem can be cast as the following non-linear system:
\begin{eqnarray}
\bzero = \cE (\tilde{\bx}) = \cE (\cB (\bx)) = \cO(\bx)
\end{eqnarray}
 where $\cO = \cE \circ \cB$.

@@

>>>>

The problem can be cast as the following non-linear system:
\begin{eqnarray}
\bzero = \cE (\tilde{\bx}) = \cE (\cB (\bx)) = \cO(\bx),
\end{eqnarray}
 where $\cO = \cE \circ \cB$.

@@

\subsection{Numerical Results}
The results for steady-state velocity $\cU$ as a function of the electric field magnitude $\beta$
are shown at Figures \ref{fig:NumResA} and \ref{fig:NumResB}. 
Since log-log scale is used, blue and red colors are used 
for positive and negative velocities, respectively.

For small $\beta$, the linear regime dominates, $\cU \propto \beta$. 
However, from a specific $\beta_c$, the nonlinear regime dominates, such that
$\cU \propto \beta^3$, until $\beta \sim O(1)$.

The theoretical results for the nonlinear regime are computed by asymptotic expansion of the
nonlinear system, as described in the following section.
\begin{figure}[htbp]
\begin{framed}
    \begin{center}
        \includegraphics[width=0.45\textwidth]{figs/A1.eps}
        \includegraphics[width=0.45\textwidth]{figs/A2.eps}
        \includegraphics[width=0.45\textwidth]{figs/A3.eps}
        \includegraphics[width=0.45\textwidth]{figs/A4.eps}
        \caption{Steady-state velocity $\cU$ as a function of the electric field magnitude $\beta$, 
        for $\gamma > 1$.}
        \label{fig:NumResA}
    \end{center}
\end{framed}
\end{figure}
\begin{figure}[htbp]
\begin{framed}
    \begin{center}
        \includegraphics[width=0.45\textwidth]{figs/B1.eps}
        \includegraphics[width=0.45\textwidth]{figs/B2.eps}
        \includegraphics[width=0.45\textwidth]{figs/B3.eps}
        \includegraphics[width=0.45\textwidth]{figs/B4.eps}
        \caption{Steady-state velocity $\cU$ as a function of the electric field magnitude $\beta$,
        for $\gamma < 1$.}
        \label{fig:NumResB}
    \end{center}
\end{framed}
\end{figure}
